PyEMMA: learning the ropes of Markov state modeling --- v\versionnumber

### 2018-07-23 manuscript.tex
inserted line breaks at sentences breaks or reasonable punctuation marks
add pyemma workflow flowchart

>>>>

\begin{figure}
\includegraphics[width=0.48\textwidth]{figures/workflowchart.pdf}
\caption{The PyEMMA workflow: The MD trajectories are processed and discretized (first row). A Markov model is estimated from the resulting discrete trajectories and validated (middle row). By iterating between data processing and MSM estimation / validation, a valid model is obtained that can be analyzed (last row).}
\label{fig:workflowchart}
\end{figure}
